Verification of Stencil Computations with Spatial Specifications

### 2016-11-02 paper.tex
starting new early section on the model

>>>>

\newcommand{\domainVal}{\mathbb{Z}_\infty}
\section{Stencil specifications}

\section{The language}

We define a simple set-theoretic denotational model of the semantics
of our stencil specification language. This has a number of purposes:
(1) it serves to explain exactly the meaning of our specifications
(2) it is 
used as the basis of the inference, checking, and synthesis algorithms
(\S~\ref{sec:analysis}); (3) justifies the equational theory and
approximations of the previous section; and (4) can be used to guide
correct implementations. The model domain is over sets of vectors
which we call \emph{index schemes}, which we introduce first before
the model in \S~\ref{subsec:model}.
